Exploring probability distributions for bivariate temporal granularities

### 2019-12-17 main.Rmd
structure change of smart meter section - talking about paradox

smart_meter <- 
  read_rds("data/sm_cust50.rds")
```

@@

**gravitas** R package [@R-gravitas] is used to facilitate the systematic exploration here. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing we should have at our disposal is to know which all cyclic time granularities we can look at exhaustively. If we consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, fortnight, month, quarter, semester, year), the following time granularities can be considered for this analysis.

```{r}
library(tsibble)
interval(smart_meter10)
smart_meter10 %>% search_gran()
```

The interval of this tsibble is 30 minutes, and hence the temporal granularities range from half-hour to year. If these options are considered too many, the most coarse temporal unit can be set to be a “month”.

@@

Now that we have the list of cyclic granularities to look at, we can visualize the distribution. From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. The distribution of energy needs to be visualized across two cyclic granularities at a time. It is equivalent to taking 2 granularities from 6, which essentially is equivalent to visualizing 30 plots.However, harmony/clash pairs can identified among those 30 pairs, to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.

@@

Figure \ref{fig:wknd-wday50} shows the quantile plot of energy consumption of 50 households. Similar quantiles for weekend and weekdays indicate that behaviors of most of these customers do not alter between weekdays and weekends.

>>>>

sm <- 
  read_rds("data/sm_cust50.rds")

smart_meter <- sm %>% as_tsibble()

smart_meter
```

@@

**gravitas** R package [@R-gravitas] is used to facilitate the systematic exploration here. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing we should have at our disposal is to know which all cyclic time granularities we can look at exhaustively. If we consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, fortnight, month, quarter, semester, year), the following time granularities can be considered for this analysis. The interval of this tsibble is 30 minutes, and hence the temporal granularities range from half-hour to year. If these options are considered too many, the most coarse temporal unit can be set to be a “month”.

```{r}
library(gravitas)
smart_meter %>% search_gran()
```

@@

Now that we have a list of cyclic granularities to look at, we should be able to compute them from the data using \autoref{}. From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. But the distribution of energy needs to be visualized across two cyclic granularities at a time. It is equivalent to taking 2 granularities from 6, which essentially is equivalent to visualizing 30 plots. However, harmony/clash pairs can be identified among those 30 pairs, to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives. We will look at few harmony pairs and see how the proposed workflow can be utilized.

Figure \ref{fig:wknd-wday50} shows the quantile plot of energy consumption of 50 households. Similar quantiles for weekend and weekdays indicate that behaviors of most of these customers do not alter between weekdays and weekends or looking at all customers together balances out the fact

@@
